Moral Foundations of U.S. Political News Organizations

### 2019-01-14 pilot_manuscript.Rmd
small updates
just some small things i noticed in our meeting

apa_table(tableprint,
          note = "something useful here",
          caption = "stuff at the top", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7))
          )
```
# Discussion

@@

## Sources
Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S. news sources. These sources were selected woting to their favorability among political partisans according to @Mitchell2014. The sources favored by liberals were *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014]. The sources favored by conservatives included *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*. Political articles referencing Brett Kavanaugh's nominatino process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script. All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].

>>>>

apa_table(tableprint,
          note = "something useful here",
          caption = "stuff at the top", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7))
          )
```

@@

Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S. news sources. These sources were selected woting to their favorability among political partisans according to @Mitchell2014. The sources favored by liberals were *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014]. The sources favored by conservatives included *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*. Political articles referencing Brett Kavanaugh's nominatino process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script. All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
